---
title: "p8105_hw1_xl2934"
author: "Xiaoyang Li"
date: "2019/9/13"
output: github_document
---

# Problem 1

Create a data frame comprised of:

* a random sample of size 8 from a standard Normal distribution
* a logical vector indicating whether elements of the sample are greater than 0
* a character vector of length 8
* a factor vector of length 8, with 3 different factor “levels”

```{r problem 1_1}
library(tidyverse)

# create data frame
df = tibble(
  var_num = rnorm(8),
  var_log = var_num > 0,
  var_cha = c("Bronx", "Brooklyn", "Manhattan", "Queens", "Staten Island","Roosevelt Island", "U thant Island", "Marble Hill" ),
  var_fac = factor(c("low", "medium", "high", "high", "medium", "low", "low", "medium"))
)

# calculate mean
mean(pull(df, var_num))
mean(pull(df, var_log))
mean(pull(df, var_cha))
mean(pull(df, var_fac))
```

After take the mean of each variable, mean functoin can work for numeric and logical variable, but it can not work for character and factor.

Apply `as.numeric` function to the logical, character, and factor variables in a code chunk.
```{r problem 1_2, eval = FALSE}
as.numeric(df$var_log)
as.numeric(df$var_cha)
as.numeric(df$var_fac)
```
According to the result, logical and factor variable can be converted to numeic but character can not. Factor are arrange by the its first character order.  


In a second code chunk:

* convert the logical vector to numeric, and multiply the random sample by the result
* convert the logical vector to a factor, and multiply the random sample by the result
* convert the logical vector to a factor and then convert the result to numeric, and multiply the random sample by the result
```{r problem 1_3}
multi1 = pull(df, var_num) * as.numeric(pull(df, var_log))
as.factor(pull(df, var_log))
multi2 = pull(df, var_num) * as.factor(pull(df, var_log))
multi3 = pull(df, var_num) * as.numeric(as.factor(pull(df, var_log)))
multi3
```


# Problem 2

Create a data frame comprised of:
* x: a random sample of size 500 from a standard Normal distribution
* y: a random sample of size 500 from a standard Normal distribution
* A logical vector indicating whether x + y > 1
* A numeric vector created by coercing the above logical vector
* A factor vector created by coercing the above logical vector

```{r problem 2_1}
# create a data frame 
df2 = tibble(
  x = rnorm(500),
  y = rnorm(500), 
  vec_log = x + y > 1,
  vec_num = as.numeric(vec_log),
  vec_fac = as.factor(vec_log),
)
```
This data frame has `r nrow(df2)` rows and `r ncol(df2)` columns. The mean of `x` is `r mean(pull(df2, x))`. The median of `x` is `r median(pull(df2, x))`. The standard deviation of `x` is `r sd(pull(df2, x))`. The proportion of cases for which `x + y > 1` is `r nrow(subset(df2, x + y >1))/500`
```{r problem 2_2}
ggplot(df2, aes(x = x, y = y, colour = vec_log)) + geom_point() 
ggsave("scatter_plot.pdf")
ggplot(df2, aes(x = x, y = y, colour = vec_num)) + geom_point() 
ggplot(df2, aes(x = x, y = y, colour = vec_fac)) + geom_point() 

```

